\subsection{Reliability}
The application should have a 100\% uptime in each designed scenario. Since the application relies on different systems API’s there is room to accept small shifts in this requirement.

\subsection{Availability}
Concerning the mobile implementations the application will be available in the App Store and Play Store, rather, the desktop implementation will be available through the web app.
Eventually, there could be implementations of the project with Xamarin.Mac and UWP on Mac and Desktop available through the App Store and Microsoft Store.

\subsection{Security}
The applications will perform every request in HTTPS to preserve the security of the user. 
Data that have to be stored in the device, will be encrypted with third-party libraries to avoid leakage of the user’s information.

\subsection{Maintainability}
The implementations will be developed with the MVVM architectural pattern allowing a modular integration of future new features or changes in the requirements. 
The application will rely on Google Maps API in order to maintain its core functionalities and not on other third-party libraries that could be deprecated in future OS versions.

\subsection{Portability}
The clients are implemented with Xamarin giving support to OS’s 3 versions older than the last one available for each platform. (iOS 9-10-11, Android 6,7,8)
The applications will rely upon the MvvmCross framework to have the ecosystem needed to share the most code across the platforms.
The web-app will be based on AngularJS.
Our back-end service will be based on AWS Cognito Identity Services to allow scalability and integration with the business logic that is required. 
Changes from the normal workflow will be addressed with AWS Lambda or EC2 instances whenever needed.